Handbook streamFind: Backend

### 2024-08-01 README.Rmd
Updated settings, articles and core

The StreamFind is developed under the project ["Flexible data analysis and workflow designer to identify chemicals in the water cycle"](https://www.bildung-forschung.digital/digitalezukunft/de/wissen/Datenkompetenzen/datenkompetenzen_wissenschaftlichen_nachwuchs/Projekte/stream_find.html) which is funded by the [Bundesministerium für Bildung und Forschung (BMBF)](https://www.bmbf.de). The development is conducted by the [Institut für Umwelt & Energie, Technik & Analytik e. V. (IUTA)](https://www.iuta.de), the [Forschungszentrum Informatik (FZI)](https://www.fzi.de/) and supporting partners. The goal of the StreamFind is the development and assembly of data processing workflows for different types of analytical data (e.g., mass spectrometry and spectroscopy) and the application of the workflows in diverse fields (e.g., environmental and quality studies of the water cycle). The StreamFind aims to stimulate the use of advanced data analysis (e.g., non-target screening, statistical analysis, etc.) in routine studies, promoting standardization of data structure and processing and easing the retrospective evaluation of data. The StreamFind platform is directed to academics but also technicians, due to the aspired comprehensive documentation, well categorized set of integrated modular functions and the embedded shiny graphical user interface.  
<br>
The StreamFind development is ongoing, please [contact us](mailto:cunha@iuta.de) for questions  or collaboration.

@@

Assuming that the [R](https://cran.r-project.org/) software is installed, the StreamFind R package can be installed from the GitHub repository via the [BiocManager](https://www.bioconductor.org/install/).

@@

<!-- For installation of the StreamFind R package, it is recommended to first install the dependencies. Besides [R](https://cran.r-project.org/) and [RTools](https://cran.r-project.org/bin/windows/Rtools/) (the latter is only applicable for Windows users), the StreamFind depends on the [patRoon](https://github.com/rickhelmus/patRoon) R package and its dependencies. The patRoon R package combines several tools for basic and advanced data processing and can be used interchangeably with the StreamFind R package. Installation instructions for patRoon and its dependencies can be found [here](https://rickhelmus.github.io/patRoon/handbook_bd/manual-installation.html#r-prerequisites). -->

<!-- Then, the StreamFind R package can be installed from the GitHub repository. -->

```{r install-streamfind, eval=FALSE}
#remotes::install_github("odea-project/StreamFind", dependencies = TRUE)
```

<!-- The supplementary [StreamFindData](https://github.com/odea-project/StreamFindData) R package holds the data used in examples and other documentation assets of the StreamFind R package and can also be installed from the GitHub repository. -->

```{r install-streamfinddata, eval=FALSE}
#remotes::install_github("odea-project/StreamFindData")
```

### Documentation

@@

# References

>>>>

The StreamFind is developed within the project ["Flexible data analysis and workflow designer to identify chemicals in the water cycle"](https://www.bildung-forschung.digital/digitalezukunft/de/wissen/Datenkompetenzen/datenkompetenzen_wissenschaftlichen_nachwuchs/Projekte/stream_find.html), which is funded by the [Bundesministerium für Bildung und Forschung (BMBF)](https://www.bmbf.de). The development is carried out by the [Institut für Umwelt & Energie, Technik & Analytik e. V. (IUTA)](https://www.iuta.de), the [Forschungszentrum Informatik (FZI)](https://www.fzi.de/) and supporting partners. The goal of the StreamFind is to develop and assemble data processing workflows for different types of analytical data (e.g., mass spectrometry and spectroscopy) and to apply the workflows in different fields (e.g., environmental and quality studies of the water cycle). StreamFind aims to stimulate the use of advanced data analysis (e.g., non-target screening, statistical analysis, etc.) in routine studies, to promote standardization of data structure and processing, and to facilitate retrospective data evaluation. The StreamFind platform is aimed at scientists, but also at technicians, due to its comprehensive documentation, its well categorized set of integrated modular functions and its embedded graphical user interface.  
<br>
The StreamFind development is ongoing, please [contact us](mailto:cunha@iuta.de) for questions or collaboration.

@@

Pre-requisites for the StreamFind are the [R](https://cran.r-project.org/) software and the [RTools](https://cran.r-project.org/bin/windows/Rtools/) (only applicable for Windows users). RTools is needed for compiling the C++ code used in the StreamFind R package. Assuming that R and RTools are installed, the StreamFind R package can be installed from the GitHub repository via the [BiocManager](https://www.bioconductor.org/install/).

@@

## Other dependencies

The StreamFind depends on other open source software to process different analytical data. For instance, for non-target screening using mass spectrometry the StreamFind uses the [patRoon](https://github.com/rickhelmus/patRoon) R package and its own dependencies. Installation instructions for patRoon and its dependencies can be found [here](https://rickhelmus.github.io/patRoon/handbook_bd/manual-installation.html#r-prerequisites). Consult the documentation for dependencies of other data types.

## Suplementary data

The supplementary [StreamFindData](https://github.com/odea-project/StreamFindData) R package holds the data used in examples and other documentation assets of the StreamFind and can also be installed from the GitHub repository.

```{r install-streamfinddata, eval=FALSE}
if (!require("BiocManager", quietly = TRUE))
  install.packages("BiocManager")
BiocManager::install("odea-project/StreamFindData")
```

## Documentation

@@

## References
